A Phenomenological Model for the Intracluster Medium that matches X-ray and Sunyaev-Zel'dovich observations

### 2013-10-02 paper1.tex
small clean-ups

In order to obtain an electron density profile that we will attach to our
simulated clusters, we use a generalized Navarro-Frank-White (GNFW) profile,
\begin{equation}
n_{\rmn{e}}(x) = \frac{n_{0}}{x^{\beta}\left[1+x^{\alpha}\right]^{\frac{\delta-\beta}{\alpha}}},
\label{eq:gnfw}
\end{equation}
where $x=R/R_{\rmn{c}}$ and $R_{\rmn{c}}$ is the cluster core radius. To reduce
the dimensionality of our fit, we fix representative values of $R_{\rmn{c}} =
0.2\, R_{500}$, $\alpha = 1$ and $\delta = 2.5$. We fit the radial density
profiles of the REXCESS sample in log-log space, separating them in the two
categories of NCCCs and CCCs as shown in Fig.~\ref{fig:gas_profiles}.  We obtain
$n_{\rmn{0,NCCC}} = 1.02\times10^{-2}$~$h_{70}^{1/2}$~cm$^{-3}$,
$n_{\rmn{0,CCC}} = 8.32\times10^{-3}$~$h_{70}^{1/2}$~cm$^{-3}$,
$\beta_{\rmn{NCCC}} = -0.093$, and $\beta_{\rmn{CCC}} = 0.592$. The resulting
fits are shown in blue and red for the NCCC and CCC population,
respectively. {\bf As a cautionary remark, we emphasize that our model is only
  valid within $R_{500}$ and more work would be needed to extrapolate it to
  larger cluster radii. Those cluster regions are characterized by a steadily
  increasing level of kinetic-to-thermal pressure support
  \citep[e.g.,][]{2009ApJ...705.1129L, 2012ApJ...758...74B}, density clumping
  \citep{2011ApJ...731L..10N, 2012arXiv1209.4082B}, and asphericity and
  ellipticity of the halo morphologies \citep{2012arXiv1209.4082B}, in
  particular beyond the virial radius where the filamentary cosmic web connects
  to the cluster interiors.}

@@

>>>>

In order to obtain an electron density profile that we will attach to our
simulated clusters, we use a generalized Navarro-Frank-White (GNFW) profile,
\begin{equation}
n_{\rmn{e}}(x) = \frac{n_{0}}{x^{\beta}\left[1+x^{\alpha}\right]^{\frac{\delta-\beta}{\alpha}}},
\label{eq:gnfw}
\end{equation}
where $x=R/R_{\rmn{c}}$ and $R_{\rmn{c}}$ is the cluster core radius. To reduce
the dimensionality of our fit, we fix representative values of $R_{\rmn{c}} =
0.2\, R_{500}$, $\alpha = 1$ and $\delta = 2.5$. We fit the radial density
profiles of the REXCESS sample in log-log space, separating them in the two
categories of NCCCs and CCCs as shown in Fig.~\ref{fig:gas_profiles}.  We obtain
$n_{\rmn{0,NCCC}} = 1.02\times10^{-2}$~$h_{70}^{1/2}$~cm$^{-3}$,
$n_{\rmn{0,CCC}} = 8.32\times10^{-3}$~$h_{70}^{1/2}$~cm$^{-3}$,
$\beta_{\rmn{NCCC}} = -0.093$, and $\beta_{\rmn{CCC}} = 0.592$. The resulting
fits are shown in blue and red for the NCCC and CCC population,
respectively.

@@

{\bf As a cautionary remark, we emphasize that our model is only valid within
  $R_{500}$ and more work is needed to extrapolate it to larger cluster
  radii. Those cluster regions are characterized by a steadily increasing level
  of kinetic-to-thermal pressure support \citep[e.g.,][]{2009ApJ...705.1129L,
    2012ApJ...758...74B}, density clumping \citep{2011ApJ...731L..10N,
    2012arXiv1209.4082B}, and asphericity and ellipticity of the halo
  morphologies \citep{2012arXiv1209.4082B}, in particular beyond the virial
  radius where the filamentary cosmic web connects to the cluster interiors.}
